Argennon: A Scalable Smart Contract Platform

### 2021-07-28 tex/sections/avm.tex
Fix some readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon Virtual Machine does not have a fixed word size. Any instruction of the AVM has
its specific word size, and the addressable memory areas are byte addressable.

@@

One important property of prefix identifiers is that while they have variable and unlimited length, they are
uniquely extractable from any sequence. Assume that we have a string of digits in base $\beta$, we
know that $k$ first digits belong to an Argennon identifier, but we don't know the value of $k$.
Algorithm~\ref{alg:prefix_id} can be used to extract the prefixed identifier uniquely. Also, we can apply this algorithm
multiple times to extract a composite identifier, for example \texttt{chunkID}, from a sequence.

%##\includegraphics[width=17cm]{../img/Alg1s.png}
\begin{algorithm}[t]
    \DontPrintSemicolon
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
    \Input{A sequence of $n$ digits in base $\beta$: $d_{1}d_{2}\dots d_{n}$ \newline
    A prefix tree: $<0,A^{(1)},A^{(2)},A^{(3)},\dots>$}
    \BlankLine
    \Output{Valid identifier prefix of the sequence.}
    \BlankLine
    \For{$i = 1$ \KwTo $n$}
    {
        \If{$(0.d_{1}d_{2}\dots d_{i})_\beta < A^{(i)}$}
        {
            \KwRet{$d_{1}d_{2}\dots d_{i}$}\;
        }
    }
    \KwRet{NIL}\;
    \caption{Finding a prefixed identifier}\label{alg:prefix_id}
\end{algorithm}

When we have a prefixed identifier, and we want to know if a sequence of digits is marked by that identifier,
we use Algorithm~\ref{alg:match_id} to match the prefixed identifier with the start of the sequence. The matching
can be done with only three comparisons and an invalid prefixed identifier can also be detected.

@@

The \texttt{methodID} field is the unique identifier of a method's bytecode that
is a composite prefix code built by concatenating an \texttt{applicationID} to
a local identifier.

@@

The Argennon Virtual Machine has five run-time data areas:
\begin{itemize}
    \item Method Area
    \item Constant Area
    \item Local Frame
    \item Operand Stack
    \item Heap
\end{itemize}
All data areas except operand stack, have their own address space. Operand stack is a
last-in-first-out (LIFO) stack and is not addressable. Every AVM instruction operates on its specific
data areas.

>>>>

The Argennon Virtual Machine does not have a fixed word size and uses \textbf{little-endian} byte order. Any
instruction of the AVM has its specific word size, and the addressable memory areas are byte addressable.

@@

One important property of prefix identifiers is that while they have variable and unlimited length, they are
uniquely extractable from any sequence. Assume that we have a string of digits in base $\beta$, we
know that the sequence starts with an Argennon identifier, but we do not know the length of that identifier.
Algorithm~\ref{alg:prefix_id} can be used to extract the prefixed identifier uniquely. Also, we can apply this algorithm
multiple times to extract a composite identifier, for example \texttt{chunkID}, from a sequence.

%##\includegraphics[width=17cm]{../img/Alg1s.png}
\begin{algorithm}[t]
    \DontPrintSemicolon
    \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
    \Input{A sequence of $n$ digits in base $\beta$: $d_{1}d_{2}\dots d_{n}$ \newline
    A prefix tree: $<A^{(1)},A^{(2)},A^{(3)},\dots>$}
    \BlankLine
    \Output{Valid identifier prefix of the sequence.}
    \BlankLine
    \For{$i = 1$ \KwTo $n$}
    {
        \If{$(0.d_{1}d_{2}\dots d_{i})_\beta < A^{(i)}$}
        {
            \KwRet{$d_{1}d_{2}\dots d_{i}$}\;
        }
    }
    \KwRet{NIL}\;
    \caption{Finding a prefixed identifier}\label{alg:prefix_id}
\end{algorithm}

When we have a prefixed identifier, and we want to know if a sequence of digits is marked by that identifier,
we use Algorithm~\ref{alg:match_id} to match the prefixed identifier with the start of the sequence. The matching
can be done with only three comparisons, and an invalid prefixed identifier can be detected and will not match
any sequence.

@@

The \texttt{methodID} field is the unique identifier of a method's bytecode, which
is a composite prefix code built by concatenating an \texttt{applicationID} to
a local identifier.

@@

The Argennon Virtual Machine has five run-time data areas:
\begin{itemize}
    \item Method Area
    \item Constant Area
    \item Local Frame
    \item Operand Stack
    \item Heap
\end{itemize}
All data areas except the operand stack, have their own address space. The operand stack is a
last-in-first-out (LIFO) stack and is not addressable. Every AVM instruction operates on its specific
data areas.
